---
title: |
  | Hysteroscopy Pathway Simulation
  | Model Outputs
author: "<a href='https://github.com/ASW-Analyst'>Andy Wilson</a><br><a href='https://transformationunit.nhs.uk/'>NHS Transformation Unit</a>"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true
    css: ../config/outputs/nhs_tu_theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, out.width = '100%')
library(here)

source(paste0(here(), "/src/requirements/packages.R"))
source(paste0(here(), "/src/model/model_run.R"))
source(paste0(here(), "/src/outputs/outputs.R"))

```

```{r logo, echo = FALSE}

htmltools::img(src = knitr::image_uri(paste0(here(), "/images/logos/TU_logo_large.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:5%; padding:10px;',
               width = "180px",
               heigth = "180px")

```

## Introduction


<br/>

## Referrals {.tabset .tabset-fade}

### Summary of Referrals

Across all of the simulations there are a median of `r referrals_summary[[1, 1]]` each year.

<br/>

### Distribution of Referrals
As the pathway is simulated multiple times this will create a range of possible outcomes and activity along the pathway. The chart below shows the distribution of referrals that are generated each year from all of the model runs.

```{r test, out.width='100%'}

referrals_hist_chart

```

<br/>

